---
title: "R_docker"
author: "Andrew Bernauer"
date: "February 16, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tibble)
library(readr)
library(stringr)
path <- "C:\\Users\\andre\\Documents\\Fantasy_app\\draft18.txt"
parse_it <- read_lines(path)

team_1 <- parse_it[2]

pick <- parse_it[3]

player_and_position <- parse_it[4]

bidding <- parse_it[5]
harper <- stringr::str_subset(string = parse_it, pattern = 'Bryce Harper')

bids <- str_subset(string = parse_it, pattern = regex('\\$[0-9]')) 
bids

picks <- str_subset(string = parse_it, pattern = regex('[[:digit:]]$'))

picks

RF <- str_subset(string = parse_it, pattern = regex('RF'))

RF

SS <- str_subset(string = parse_it, pattern = regex('SS'))

SS

first <- str_subset(string = parse_it, pattern = regex('1B')) 

first

second <- str_subset(string = parse_it, pattern = regex('2B'))
 
second

third <- str_subset(string = parse_it, pattern = regex('3B'))

third

catcher <- str_subset(string = parse_it, pattern = regex('C$'))

catcher

starting_pitcher <- str_subset(string = parse_it, pattern = regex('SP'))

starting_pitcher

relief_pitcher <- str_subset(string = parse_it, pattern = regex('RP'))

relief_pitcher

center_field <- str_subset(string = parse_it, pattern = regex('CF'))

center_field

left_field <- str_subset(string = parse_it, pattern = regex('LF'))

left_field 

designated_hitter <- str_subset(string = parse_it, pattern = regex('DH'))

designated_hitter

extract_pos <- function(data, ...) {
  dots <- list(...)
  n_dots <- length(dots)
  
  stringr::str_subset(string = data, pattern = regex())
  
}

pick_2 <- str_subset(string = parse_it, '^[0-9]+$')

pick_2

picks_kershaw <- as.integer(pick_2[1:19])

picks_kershaw 

bids_kershaw <- bids[1:19]

bids_kershaw

players_kershaw <- c(RF[1], starting_pitcher[1], RF[2], second[1], starting_pitcher[2], starting_pitcher[3], third[1], starting_pitcher[4], third[2], starting_pitcher[5], starting_pitcher[6], relief_pitcher[1], relief_pitcher[2], third[3], RF[3], second[2], SS[1], first[1], catcher[1])

players_kershaw


kershank_df <- data.frame( NO. = picks_kershaw,
                              PLAYER = players_kershaw,
                              BID_AMOUNT = bids_kershaw
  
)
structure(kershank_df)

picks_choo_talkin <- as.integer(pick_2[20:38])

bids_choo_talkin <- bids[20:38]

bids_choo_talkin

players_choo_talkin <- c(starting_pitcher[7], first[2], starting_pitcher[8], starting_pitcher[9], catcher[2], third[4], left_field[1], SS[2], second[3], second[4], relief_pitcher[3], first[3], relief_pitcher[4], relief_pitcher[5], left_field[2], center_field[1], center_field[2], starting_pitcher[10], center_field[3])

Choo_talkin_df <- data.frame(NO. = picks_choo_talkin,
                             PLAYER = players_choo_talkin, 
                             BID_AMOUNT = bids_choo_talkin
                             )
Choo_talkin_df 

picks_beavens <- as.integer(pick_2[39:57])

picks_beavens

bids_beavens <- bids[39:57]

players_beavens <- c(SS[3], starting_pitcher[11], relief_pitcher[6], third[5], catcher[3], left_field[3], SS[4], starting_pitcher[12], starting_pitcher[13], center_field[4], first[4], second[5], first[5], relief_pitcher[7], left_field[4], designated_hitter[2], SS[5], starting_pitcher[14], RF[4])

team_beavens_df <- data.frame(NO. = picks_beavens, 
                              PLAYER = players_beavens, 
                              BID_AMOUNT = bids_beavens)

team_beavens_df