---
title: "R_Shiny_data_prep"
author: "Andrew Bernauer"
date: "February 16, 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#library(errorist)
library(tibble)
library(readr)
library(stringr)
path <- "C:\\Users\\andre\\Documents\\Fantasy_app\\data\\draft18.txt"
parse_it <- read_lines(path)

team_1 <- parse_it[2]

pick <- parse_it[3]

player_and_position <- parse_it[4]

bidding <- parse_it[5]
harper <- stringr::str_subset(string = parse_it, pattern = 'Bryce Harper')

bids <- str_subset(string = parse_it, pattern = regex('\\$[0-9]')) 
bids

picks <- str_subset(string = parse_it, pattern = regex('[[:digit:]]$'))

picks

RF <- str_subset(string = parse_it, pattern = regex('RF'))

RF

SS <- str_subset(string = parse_it, pattern = regex('SS'))

SS

first <- str_subset(string = parse_it, pattern = regex('1B')) 

first

second <- str_subset(string = parse_it, pattern = regex('2B'))
 
second

third <- str_subset(string = parse_it, pattern = regex('3B'))

third

catcher <- str_subset(string = parse_it, pattern = regex('C$'))

catcher

starting_pitcher <- str_subset(string = parse_it, pattern = regex('SP'))

starting_pitcher

relief_pitcher <- str_subset(string = parse_it, pattern = regex('RP'))

relief_pitcher

center_field <- str_subset(string = parse_it, pattern = regex('CF'))

center_field

left_field <- str_subset(string = parse_it, pattern = regex('LF'))

left_field 

designated_hitter <- str_subset(string = parse_it, pattern = regex('DH'))

designated_hitter

extract_pos <- function(data, ...) {
  dots <- list(...)
  n_dots <- length(dots)
  
  stringr::str_subset(string = data, pattern = regex())
  
}

pick_2 <- str_subset(string = parse_it, '^[0-9]+$')

pick_2

picks_kershaw <- as.integer(pick_2[1:19])

picks_kershaw 

bids_kershaw <- bids[1:19]

bids_kershaw

players_kershaw <- c(RF[1], starting_pitcher[1], RF[2], second[1], starting_pitcher[2], starting_pitcher[3], third[1], starting_pitcher[4], third[2], starting_pitcher[5], starting_pitcher[6], relief_pitcher[1], relief_pitcher[2], third[3], RF[3], second[2], SS[1], first[1], catcher[1])

players_kershaw


kershank_df <- data.frame( NO. = picks_kershaw,
                              PLAYER = players_kershaw,
                              BID_AMOUNT = bids_kershaw,
                           stringsAsFactors = FALSE
  
)
structure(kershank_df)

picks_choo_talkin <- as.integer(pick_2[20:38])

bids_choo_talkin <- bids[20:38]

bids_choo_talkin

players_choo_talkin <- c(starting_pitcher[7], first[2], starting_pitcher[8], starting_pitcher[9], catcher[2], third[4], left_field[1], SS[2], second[3], second[4], relief_pitcher[3], first[3], relief_pitcher[4], relief_pitcher[5], left_field[2], center_field[1], center_field[2], starting_pitcher[10], center_field[3])

Choo_talkin_df <- data.frame(NO. = picks_choo_talkin,
                             PLAYER = players_choo_talkin, 
                             BID_AMOUNT = bids_choo_talkin,
                             stringsAsFactors = FALSE
                             )
Choo_talkin_df 

Choo_talkin_tibble <- as_tibble(Choo_talkin_df)

picks_beavens <- as.integer(pick_2[39:57])

picks_beavens

bids_beavens <- bids[39:57]

players_beavens <- c(SS[3], starting_pitcher[11], relief_pitcher[6], third[5], catcher[3], left_field[3], SS[4], starting_pitcher[12], starting_pitcher[13], center_field[4], first[4], second[5], first[5], relief_pitcher[7], left_field[4], designated_hitter[1], SS[5], starting_pitcher[14], RF[4])

team_beavens_df <- data.frame(NO. = picks_beavens, 
                              PLAYER = players_beavens, 
                              BID_AMOUNT = bids_beavens,
                              stringsAsFactors = FALSE)

team_beavens_df

picks_Tyrone <- as.integer(pick_2[58:76])

bids_Tyrone <- bids[58:76]

players_Tyrone <- c(third[6], starting_pitcher[15], first[6], SS[6],  first[7], second[6], starting_pitcher[16], second[7], SS[7], RF[5], catcher[4], catcher[5], relief_pitcher[8], starting_pitcher[17], starting_pitcher[18], starting_pitcher[19], RF[6], relief_pitcher[9], starting_pitcher[20])

tyrone_df <- data.frame(NO. = picks_Tyrone, 
                       PLAYER = players_Tyrone,
                       BID_AMOUNT = bids_Tyrone,
                      stringsAsFactors = FALSE)

tyrone_df

picks_Mckenna <- as.integer(pick_2[77:95])

bids_Mckenna <- bids[77:95] 

players_Mckenna <- c(center_field[5], starting_pitcher[21], center_field[6], third[7], catcher[6], first[8], relief_pitcher[10], center_field[7], starting_pitcher[22], first[9], starting_pitcher[23], starting_pitcher[24], first[10], relief_pitcher[11], second[8], third[8], starting_pitcher[25], SS[8], second[9])


Mckenna_df <- data.frame(NO. = picks_Mckenna,
                         PlAYER = players_Mckenna, 
                         BID_AMOUNT = bids_Mckenna, 
                         stringsAsFactors = FALSE)

Mckenna_df

Bartolos_votos_picks <- as.integer(pick_2[96:114])
Bartolos_votos_picks

Bartolos_votos_bids <- bids[96:114]

Bartolos_votos_players <- c(third[9], starting_pitcher[26], third[10], left_field[5], left_field[6], starting_pitcher[27], starting_pitcher[28], RF[7], relief_pitcher[12], second[10], SS[9], first[11], SS[10], starting_pitcher[29], catcher[7], SS[11], first[12], starting_pitcher[30], relief_pitcher[13] )

bartolos_df <- data.frame(NO. = Bartolos_votos_picks,
                          PLAYER = Bartolos_votos_players,
                          BID_AMOUNT = Bartolos_votos_bids,
                          stringsAsFactors = FALSE
                          )

bartolos_df
Shane_Beliebers_picks <- as.integer(pick_2[115:133])

Shane_Beliebers_bids <- bids[115:133]

Shane_Beliebers_players <- c(SS[12], second[11], second[12], center_field[8], center_field[9], center_field[10],   starting_pitcher[31], starting_pitcher[32], starting_pitcher[33], first[13], second[13], catcher[8], first[14], SS[13], third[11], starting_pitcher[34], starting_pitcher[35], relief_pitcher[14], relief_pitcher[15])

Shane_beliebers_df <- data.frame(NO. = Shane_Beliebers_picks,
PLAYER = Shane_Beliebers_players,
BID_AMOUNT = Shane_Beliebers_bids,
stringsAsFactors = FALSE)

Shane_beliebers_df

A_Rod_picks <- as.integer(pick_2[134:152])

A_Rod_bids <- bids[134:152]

A_Rod_players <- c(first[15], starting_pitcher[36], SS[14], second[14], third[12], third[13], center_field[11], SS[15], left_field[7], catcher[9], left_field[8], third[14], center_field[12], relief_pitcher[16], first[16], starting_pitcher[37],  relief_pitcher[17], RF[8], starting_pitcher[38])

A_Rod_df <- data.frame(NO. =  A_Rod_picks,
                       PLAYER = A_Rod_players,
                       BID_AMOUNT = A_Rod_bids,
                       stringsAsFactors = FALSE)

A_Rod_df


Sniffers_Row_picks <- as.integer(pick_2[153:171])

Sniffers_Row_bids <- bids[153:171]

Sniffers_Row_players <- c(third[15], RF[9], RF[10], starting_pitcher[39], starting_pitcher[40], first[17], starting_pitcher[41], starting_pitcher[42], starting_pitcher[43], first[18], RF[11], RF[12], relief_pitcher[18], starting_pitcher[44], relief_pitcher[19], SS[16], second[15], SS[17], catcher[10])

Sniffers_Row_df <- data.frame(NO. = Sniffers_Row_picks,
                              PLAYER = Sniffers_Row_players,
                              BID_AMOUNT = Sniffers_Row_bids, 
                              stringsAsFactors = FALSE)

Sniffers_Row_df

Team_Christy_picks <- as.integer(pick_2[172:190])

Team_Christy_bids <- bids[172:190]

Team_Christy_players <- c(first[19], left_field[9], starting_pitcher[45], SS[18], starting_pitcher[46], starting_pitcher[47], second[16], third[16], center_field[13], center_field[14], SS[19], relief_pitcher[20], first[20], starting_pitcher[48], RF[13], starting_pitcher[49], left_field[10], relief_pitcher[21], catcher[11])

Team_Christy_df <- data.frame(NO. = Team_Christy_picks,
                              PLAYER = Team_Christy_players,
                              BID_AMOUNT = Team_Christy_bids,
                              stringsAsFactors = FALSE
                              
                              )

Team_Christy_df
Long_Ball_picks <- as.integer(pick_2[191:209])


Long_Ball_bids <- bids[191:209]

Long_Ball_players <- c(second[17], designated_hitter[2], first[21], first[22], starting_pitcher[50], starting_pitcher[51], relief_pitcher[22], starting_pitcher[52], left_field[11], left_field[12], SS[20], relief_pitcher[23], starting_pitcher[53], third[17], left_field[13], second[18], first[23], starting_pitcher[54], catcher[12] )

Long_Ball_df <- data.frame(NO. = Long_Ball_picks, 
                           PLAYER = Long_Ball_players,
                           BID_AMOUNT = Long_Ball_bids,
                           stringsAsFactors = FALSE)
Long_Ball_df


The_Wright_picks <- as.integer(pick_2[210:228])

The_Wright_picks
The_Wright_bids <- bids[210:228]
The_Wright_bids

The_Wright_Player <- c(RF[14], center_field[15], starting_pitcher[55], first[24], starting_pitcher[56], first[25], third[18], SS[21], starting_pitcher[57], left_field[14], catcher[13], SS[22], starting_pitcher[58], second[19], center_field[16], third[19], relief_pitcher[24], center_field[17], relief_pitcher[25])

The_Wright_Player_df <- data.frame(NO. = The_Wright_picks,
                                   PLAYER = The_Wright_Player,
                                   BID_AMOUNT = The_Wright_bids,
                                   stringsAsFactors = FALSE)
The_Wright_Player_df

LoadToEnvironment <- function(RData, env = new.env()) {
  load(RData, env)
  return(env)
}

saveRDS(Shane_beliebers_df,  file = "beliebers.rds")
saveRDS(kershank_df, file = "kshank.rds")
saveRDS(Choo_talkin_df, file = "choo.rds")
saveRDS(team_beavens_df, file = "beavens.rds")
saveRDS(tyrone_df, file = "tyrone.rds")
saveRDS(Mckenna_df, file = "mckenna.rds")
saveRDS(bartolos_df, file = "bartolos.rds")
saveRDS(A_Rod_df, file = "ARod.rds")
saveRDS(Sniffers_Row_df, file = "Sniffersrow.rds")
saveRDS(Team_Christy_df, file = "Team_christy.rds")
saveRDS(Long_Ball_df, file = "Long_Ball.rds")
saveRDS(The_Wright_Player_df, file = "The_Wright.rds")